### 2019-02-18 manuscript/main.tex
small tex matters
notes to self, and linebreaks to aid diff
done editing Methods
- minor changes (typos) noted at compilation - added ramanauskas2017 to replace igic2001

\documentclass[11pt]{article}
\usepackage{evolution}
\usepackage{hyperref}

@@

\begin{center}
    \textbf{When your favorite trait is not enough to explain diversification: An example of diversification linked to polyploidy and breeding system in Solanaceae}
\end{center}

@@

\noindent
Rosana Zenil-Ferguson,%
\endnote{University of Minnesota Twin Cities}
%
\noindent
J. Gordon Burleigh,%
\endnote{University of Florida}
%
\noindent
William A. Freyman,%
\endnote{23 and me}
%
\noindent
Boris Igi\'c,%
\endnote{University of Illinois}
%
\noindent
Itay Mayrose,%
\endnote{Tel Aviv University}
%
and
Emma E. Goldberg%
\endnote{University of Minnesota Twin Cities}

@@

\noindent
\textit{Running head:} Polyploidy and breeding systems Solanaceae

@@

@@

\setstretch{1}
\bibliography{refs}
\bibliographystyle{evolution}
\setstretch{\stretchby}

>>>>

\documentclass[11pt]{article}
\usepackage{evolution}

@@

% Accumulate ideas for titles here...
%
% When your favorite trait is not enough to explain diversification: An example of diversification linked to polyploidy and breeding system in Solanaceae % E: Fun, but I think we need something more formal
%
% New comparative approaches for the study of breeding system, polyploidy, and lineage diversification % E: the tentative title given to New Phyt
%
% Comparative study of breeding system, ploidy, and lineage diversification % E: too boring?
%
% Interacting effects of ploidy and breeding system on lineage diversification % E: but "effects" is too causal

\begin{center}
    \textbf{Interacting associations between ploidy, breeding system, and lineage diversification}
\end{center}

@@

\noindent
Rosana Zenil-Ferguson,%
\endnote{University of Minnesota Twin Cities}
%
\noindent
J.~Gordon Burleigh,%
\endnote{University of Florida}
%
\noindent
William A.~Freyman,%
\endnote{23 and me}
%
\noindent
Boris Igi\'c,%
\endnote{University of Illinois}
%
\noindent
Itay Mayrose,%
\endnote{Tel Aviv University}
%
and
Emma E.~Goldberg%
\endnote{University of Minnesota Twin Cities}

@@

\noindent
\textit{Running head:} Ploidy and breeding systems in Solanaceae
% E: I've been changing "polyploidy" to "ploidy" in various places because "polyploidy" is one state of the "ploidy" trait, just as "SI" is one state of the "breeding system" trait

@@

NSF DEB-1655478.
The Minnesota Supercomputing Institute (MSI) at the University of Minnesota provided computing resources for this project.

@@

\setstretch{1}
\bibliography{refs}
\bibliographystyle{evolution} % E: remove URLs
\setstretch{\stretchby}
